\chapter{Introduction}
% \begin{figure}
%     \incfig{test}
%     \caption{Just a test diagram}
% \end{figure}
% \begin{figure}
%     \incfig{figure2} 
%     \caption{Abstract Art}
% \end{figure}

% \begin{figure}
%     \label{fig:monopulse}
%     \incfig{monopulse}
%     \caption{A monopulse radar}
% \end{figure}

% \begin{figure}
%     \incfig[1]{monopulse2}
%     \caption{A diagram of a monopulse radar}
% \end{figure}

% \input{Sections/Ch1 Introduction/motivation.tex}
% \input{Sections/Ch1 Introduction/knowledge_gaps.tex}
% \input{Sections/Ch1 Introduction/contributions.tex}
With more uncrewed aerial vehicles (UAVs) in the air each year, and a growing desire 
for them to operate in controlled airspaces, there is a concern regarding their ability 
to maintain separation from hazards in the air. United States and European federal 
agencies are developing policy that necessitates detect-and-avoid (DAA) systems for 
UAVs, which parallel the visual and instrument flight rules (VFR \& IFR) that dictate 
how human pilots avoid traffic \cite{easa_easy_access_uas_2024} \cite{rtca_sc228_2025} 
\cite{serres_wu_2021_nasa_tm}.

While some proposed DAA systems utilise optical and infrared sensors 
\cite{serres_wu_2021_nasa_tm}, radar sensors may also be suitable, as they can perform 
sensing over great distances in all weather conditions, due to their relatively low 
atmospheric attenuation \cite{borden_radar_imaging_airborne_targets_1999}. The 
inconvenient side effect of their long wavelength property is that angular resolution 
is much lower compared to similarly sized optical systems. If the challenges stemming 
from this limitation are overcome, the implementation of radar as the primary sensing 
mode or an additional sensing mode will improve the perception capabilities, and thus 
the safety, of UAVs.

Historically, airborne radar has been used for large aircraft, where size weight and 
power (SWaP) constraints are not strict. The size and weight of radar systems has been 
the largest barrier to their use on smaller platforms, \cite{Lies2020}, \cite{McLain2015},
\cite{Wang2016}. This historical constraint is now weakening because both sides of the 
radar stack have miniaturised. Texas Instrument's AWR2243 is a single 76-81 GHz radar chip 
that integrates phase-locked loops (PLLs), three transmitters, four receivers, a mixer, an 
ADC, and self calibration, all on a 10.4mm $\times$ 10.4mm printed circuit board (PCB)
-friendly package. Higher frequency, lower noise, electronics and the miniaturisation of 
the transistor have been key enablers of this technology. Higher frequency radar allows of 
higher resolution imaging or smaller aperture; lower noise allows for an increase 
sensitivity to targets. On the compute side, modern UAV systems often have a dedicated, 
high compute companion computer in addition to the flight compute. NVIDIA's Jetson series 
computers such as Xavier NX, Orin Nano and Orin NX providing up 21, 67, 157 trillion 
operations per second (TOPS) on 8-bit integers respectively, while each weighting under 
50g (without a heat sink). 

Plextek’s mmWave-based 60 GHz sense-and-avoid radar for UAVs demonstrates the feasibility 
of pairing miniaturised radar hardware with modern edge computing for the detection of 
people, vehicles, poles, and buildings at ranges of hundreds of metres \cite{}. Echodyne's 
EchoFlight, a 817 g commercial radar systems for UAVs that can detect small drone targets 
at a range of 750 m, reflects the onset of the technology into industry \cite{Echodyne2024}. The wider UAV market shows a similar shift toward more computationally 
demanding onboard tasks. Skydio’s X10, for instance, incorporates both an NVIDIA Jetson 
Orin SoC and a Qualcomm QRB5165 SoC within a 2.11 kg platform while retaining up to 40 
minutes of flight time \cite{}, illustrating that substantial embedded compute is now 
compatible with practical UAV SWaP limits. These developments suggest that recent 
improvements in radar miniaturisation and embedded heterogeneous computing are promoting a 
new class of computation-heavy UAV sensing systems, making it timely to revisit radar 
target tracking and to determine the most suitable signal-processing pipeline for UAV 
detect-and-avoid applications. 

Despite the challenges, UAVs are the fastest growing market for radar systems, projected 
to grow with a compound annual growth rate (CAGR) of 11.22\% globally through 2030 \cite{mordor_airborne_radars_market_2025}. To make these emerging radar systems more 
performant, accessible, and safe, it would be valuable to find the most suitable radar 
signal processing pipeline for UAV DAA systems, revisiting the old problem of radar target 
tracking in the face of unique hardware conditions.

Software-defined architecture (SDAs) are increasingly preferred over hardware defined 
radar systems for UAV applications as software modifications can be shipped faster than 
hardware modifications \cite{mordor_airborne_radars_market_2025}. As a result, graphics 
processing units (GPUs) are favoured over non-programmable digital signal processors such 
as application specific integrated circuits (ASICs). GPU-accelerated implementations are 
also favourable for computationally intensive stages of the radar processing chain, as 
many core operations, such as fast Fourier transforms (FFTs) and matrix operations, are 
highly data-parallel, allowing for large increases in throughput when compared to serial 
processors. Additionally, GPU-based pipelines can leverage mature developer friendly, GPU 
software ecosystems and optimised libraries \cite{zaknoun2024_gpu_radar}. Additionally, 
the incorporation of AI into radar tracking algorithms has further encouraged these highly 
parallel, GPU-based pipelines \cite{electronics13214251}. Key open questions remain around 
balancing the compute saved through GPU parallelism against the cost of data movement and 
synchronisation, and how unified (shared) CPU--GPU memory on embedded platforms changes 
this trade-off. 

Given the miniaturisation of radar enabling technology, the potential benefits for radar 
base DAA systems, and the range limitations of systems suitable for small radar systems. 
This report proposes a software pipeline design that allows for the radar tracking of 
aerial hazards on UAVs with strict SWaP constraints. Particular emphasis will be placed on 
maximising the sensitivity to faraway targets, a requirement for operating in shared 
airspace, and minimising computation resources and latency. 

The literature reviewed in Chapter \ref{ch:literature_review} collectively demonstrates 
that compact radar hardware is now sufficiently mature for UAV DAA applications. 
SWaP-compliant systems have been built, detection at DAA-relevant ranges has been 
achieved, and processing feasibility on constrained embedded platforms has been 
established. However, three important gaps are identified.

First, existing hardware demonstrations validate detection only against large, 
high radar cross-section targets such as buildings and fixed-wing aircraft, 
leaving the practical sensitivity floor of compact UAV radar systems against 
small moving airborne targets unknown.

Second, no work has benchmarked a GPU-based radar pipeline in a UAV DAA 
setting. Existing studies are limited to FPGA and ARM CPU implementations, 
evaluate single algorithm sequences on single hardware configurations, and do 
not profile architectural bottlenecks such as host--device data transfer and 
thread synchronisation overhead.

Third, sensitivity algorithms for low-SNR monopulse radar have only been 
validated under idealised white Gaussian noise with single simulated targets, 
and none have been integrated into a complete end-to-end range--Doppler 
tracking pipeline.

The core problem this thesis addresses is the absence of a principled, 
hardware-aware understanding of how algorithm selection and implementation 
choices jointly affect the sensitivity and computational performance of compact 
monopulse radar systems for UAV DAA. This thesis constructs that understanding 
through a systems-level investigation of the software design space of a 
GPU-based radar tracking pipeline, with specific contributions as follows:

\begin{itemize}
    \item A comparison of the algorithms necessary for monopulse radar, 
    assessed by detection sensitivity and track quality 
    in multi-target aerial scenarios, to inform algorithm selection.
    \item A comparison of alternative low-level implementations of the selected 
    algorithms, quantifying their effects on end-to-end throughput and latency 
    in highly parallelised GPU pipelines, to inform implementation choices.
    \item An assessment of how these algorithm and implementation conclusions 
    vary across embedded hardware configurations, providing hardware-aware 
    design recommendations.
\end{itemize}

This thesis concerns the software design and evaluation of radar tracking 
pipelines for UAV DAA under SWaP constraints. The scope is limited to 
processing stages occurring after radar sample acquisition, with emphasis on 
how alternative signal-processing, angle-estimation, and tracking algorithms 
perform on embedded compute platforms suitable for small and medium UAVs. 
The processing chain considered spans front-end windowing, FFT, coherent 
integration, CFAR detection, monopulse angle estimation, coordinate 
transformation, data association, tracking filters, and track management, 
together with orchestration decisions such as batching, host--device transfers, 
and synchronisation overhead.

Several topics are outside scope. Radar front-end hardware design, full-scale 
field trials, FPGA and ASIC implementations, and cross-modality comparisons 
with optical or infrared sensing are not addressed. The thesis does not claim 
certification readiness for operational deployment; rather, it provides 
comparative evidence and design guidance for onboard radar processing under 
realistic embedded constraints.

The thesis proceeds under three assumptions. The radar sensor is a small 
conformal monopulse radar whose aperture and power budget are representative 
of a UAV-compatible installation. The target compute platform is GPU-enabled 
embedded hardware, reflecting the increasing use of heterogeneous CPU/GPU 
companion computers in modern UAV systems. The hardware context of primary 
interest features shared or unified CPU/GPU memory, as found in many embedded 
systems-on-module, though comparison against CPU-only and discrete-memory 
configurations is used where available to clarify architectural trade-offs.

\input{Sections/Ch1 Introduction/thesis_structure.tex}

This project targets a practical gap between established airborne radar 
tracking methods, which are typically developed and validated for large apertures 
and well-provisioned platforms, and the constraints of small to medium UAV payloads. 
By evaluating both algorithmic choices and low-level implementations on GPU-enabled 
embedded hardware, this work provides an evidence-based reference for software-defined 
radar processing under SWaP constraints. The resulting design recommendations and 
benchmarking methodology are intended to be reusable by future UAV radar efforts, 
improving the comparability of results across the field. Evidence of achievable 
detection and tracking performance under these constraints can also inform 
requirements for DAA capability, supporting the safer integration of UAVs into 
controlled airspace \cite{utm_action_plan_2024}.

