\section{Processing Application}
\todo{Discuss the results for each of the operations. relate to our contributions, gaps and results from the other areas of research.}

\subsection{Windowing Operation}
\begin{itemize}
    \item Discuss the effects that the different windowing functions have the reliability of CFAR on the synthetic dataset, and the real-world dataset.
    \item Discuss the computational performance of the different windowing functions, and how this affects the overall performance of the pipeline.
    \item Discuss the implications of these results for the design of radar processing pipelines, and how they inform our understanding of the trade-offs between different windowing functions in terms of detection performance and computational efficiency.
\end{itemize}

\subsection{Coherent Integration Operation}
\begin{itemize}
    \item Discuss the effects that the different coherent integration window sizes have on the SNR of the output, and how this affects the sensitivity of the target to CFAR detection on the synthetic dataset. 
    \item Discuss the computational performance of the different coherent integration window sizes, and how this affects the overall performance of the pipeline.
    \item Discuss the implications of these results for the design of radar processing pipelines, and how they inform our understanding of the trade-offs between different coherent integration window sizes in terms of time resolution, computational efficiency, and detection performance.
\end{itemize}