\section{Low SWaP Aerial Radar}
% Important works in order of importance.  
% - Lies2020 - haven't analysed yet
% - Wang2016 - haven't analysed yet
% - Sysak2025
Sysak et al. \cite{sysak2025_lightweight_compact_pulse_radar_uav_collision_avoidance} present a lightweight X-band monopulse radar designed explicitly for mid-air collision avoidance on medium UAV platforms, addressing the range shortfall that often limits compact frequency modulated continuous wave (FMCW)-based solutions. Their system integrates a multi-channel, forward-looking antenna with an FPGA-based pulse compression on a single 60 gram PCB, enabling online range processing and adaptive CA-CFAR detection, while keeping average power consumption below 80 Watts. Field trials in urban environments demonstrate reliable detection of large obstacles at 1–3 km, providing manoeuvring standoff times on the order of tens of seconds. Successful open air field tests against large fixed-wing moving targets were conducted demonstrate strong target visibility on a 3.15m-wide target 6.5 kilometres away. This work produced results that impact this thesis' work, demonstrating that high-performance, long distance sensing can be achieved under strict SWaP constraints with a pulsed, multi-channel architecture. On top of this, the work validates a simple online software pipeline from range compression to Time to Closest Point of Approach (TCPA) estimation, which is a critical component of the proposed research. 

One weakness of the work is that the validation is conducted against large, high-cross-section targets, such as buildings and aircraft with larger reflective wings. The system's sensitivity to small airborne targets in realistic encounter conditions is not characterised. Additionally, while the work acts as a proof of concept for UAV radar systems, it does not provide details on the system latency, an important metric for real-time DAA applications. 

Wang et al. \cite{Wang2016}, demonstrate a complete low-SWaP Linear Frequency Modulated Continuous Wave (LFMCW) multi target tracker design for medium to large (10-600kg) UAV platforms for detecting drones of all sizes within a similar range, but performance is only validated in simulation. While the work details its software architecture, the lack of latency, throughput, and sensitivity benchmarking leaves open questions about the suitability of the proposed pipeline for real-time DAA applications. 

The proposed project builds off of the work of Sysak et al. and Wang et al. by measuring system sensitivity to small moving targets vs large moving targets. By investigating GPU-oriented implementations of radar algorithms, and the effect that software choices have on the system's computational performance and sensitivity to small targets, the proposed research will provide a more software-conscious and complete understanding of the feasibility and capabilities of UAV radar systems. 

\subsection{End-to-end UAV DAA onboard processing pipelines}
Feasibility studies with more emphasis on the radar DAA processing pipelines have been documented. Three that are especially notable include the systems designed by Shi et al. \cite{6712628}, Moses et al. \cite{6044363}, and Newmeyer et al. \cite{7577322}. Shi et al, similarly motivated by the need to detect-and-avoid non-cooperative targets, describe the design of a small FMCW phased array built mainly from off-the-shelf development boards. The design is only suitable for large UAVs proposed project will target smaller platforms. Additionally, the full radar processing was not entirely onboard and online, splitting steps between an onboard FPGA and offboard post processing. On the other hand, the proposed research will design the software for fully onboard, online tracking. 

Moses et al. illustrate the capabilities of a lightweight, single channel FMCW radar. Testing was performed on a quadcopter. A major component of their analysis emphasises identification via micro-Doppler modulation, which is largely evaluated through Doppler-domain signatures over end-to-end range--Doppler detection and tracking. While this is well motivated for classification, it doesn't address the tracking targets in the  range--Doppler space. It also remains unclear how the small aperture and SWaP limits affect range-domain SNR, achievable range resolution, and the resulting false alarm behaviour. The proposed research fills this gap by benchmarking range--Doppler processing, CFAR detection, monopulse angle estimation, and multi-target tracking in low-SNR regimes, and by quantifying how these choices trade sensitivity against latency and throughput on embedded GPU hardware. 

Finally, Newmeyer et al. demonstrated a 120 gram, 8 Watt FMCW phased array radar and processing pipeline that utilised the FPGA fabric on a Zynq ARM CPU. Power, compute cost, latency distributions, and hardware resources were closely monitored, and the project clearly demonstrates that radar DAA systems can operate under strict SWaP constraints. However, the study only evaluates one hardware configuration, and one radar algorithm sequence. The proposed research fills this gap by systematically comparing alternative algorithmic pathways and low-level implementations, and by evaluating how pipeline bottlenecks and end-to-end performance change across different embedded compute and memory configurations, including GPU-based architectures. 

While these works demonstrate early feasibility of small-platform DAA radar, their hardware stacks are not fully representative of modern embedded radar processing platforms in the sense that they do not utilise GPUs or occur entirely onboard, and their evaluations do not explore how algorithmic selection relates to sensitivity to faint target signals. Consequently, there remains a gap in the literature regarding how to integrate and benchmark alternative radar processing and tracking algorithms for small conformal apertures under SWaP constraints, particularly when optimising jointly for sensitivity, latency, and throughput. 
