\chapter{Literature Review}
\label{ch:literature_review}
% \input{Sections/Ch3 Literature Review/Low SWaP Aerial Radar.tex}
% \input{Sections/Ch3 Literature Review/GPU radar processing performance.tex}
% \input{Sections/Ch3 Literature Review/Low SNR Monopulse feasability.tex}
% \input{Sections/Ch3 Literature Review/Programmable Vision Acceleration for Radar.tex}
% \input{Sections/Ch3 Literature Review/Summary.tex}

\section{Compact Airborne Radar for UAV DAA}

Early demonstrations established that capable radar sensing is achievable 
under UAV SWaP constraints. Sysak et al.\ 
\cite{sysak2025_lightweight_compact_pulse_radar_uav_collision_avoidance} 
present a lightweight X-band monopulse radar for mid-air collision avoidance 
on medium UAV platforms, integrating a multi-channel forward-looking antenna 
with FPGA-based pulse compression on a single 60 gram PCB, with average power 
below 80 Watts. Field trials demonstrate reliable detection of large obstacles 
at 1--3 km, and the work validates a simple online pipeline from range 
compression to TCPA estimation. However, validation is conducted exclusively 
against large, high radar cross-section targets, and system latency is not 
reported. This thesis addresses these gaps by characterising detection 
sensitivity against small moving airborne targets and by measuring end-to-end 
pipeline latency on embedded hardware.

Wang et al.\ \cite{Wang2016} demonstrate a complete low-SWaP LFMCW system for 
group 2/3 UAS incorporating FFT-based detection, digital beamforming, 
multi-target tracking, and GPU-accelerated FFT for update rate improvement. 
However, performance is validated in simulation only, with no latency 
measurements, no throughput figures, and no benchmarking of the GPU claim. 
This thesis addresses these gaps by providing hardware-validated latency and 
throughput measurements for a comparable pipeline, and by substantiating the 
GPU acceleration argument with systematic benchmarks.

Moses et al.\ \cite{6044363} introduce a 230 gram miniature radar mountable 
on a small quadcopter, demonstrating that radar hardware can be integrated onto 
very small platforms. Their evaluation emphasises target identification via 
micro-Doppler signatures rather than ranging or tracking, leaving open 
questions about how the small aperture affects range-domain SNR, range 
resolution, and false alarm behaviour. This thesis addresses this gap by 
benchmarking range--Doppler processing, CFAR detection, and multi-target 
tracking under the SNR conditions characteristic of small-aperture UAV radars.


\section{Embedded Radar Processing Under SWaP Constraints}

Shi et al.\ \cite{6712628} describe a small FMCW phased array built from 
off-the-shelf development boards, validating that continuous real-time 2D FFTs 
are achievable on a 100 MHz FPGA. However, processing was split between an 
onboard FPGA and offboard post-processing, and signal coherence problems 
prevented real-world validation. This thesis addresses this gap by implementing 
a fully onboard, online pipeline and validating it against real target returns.

Newmeyer et al.\ \cite{7577322} demonstrated a 120 gram, 8 Watt FMCW phased 
array pipeline on a Zynq ARM CPU, closely monitoring power, latency 
distributions, and hardware resources. This work clearly establishes that 
radar DAA can operate under strict SWaP constraints. However, only one 
hardware configuration and one algorithm sequence are evaluated. This thesis 
addresses this gap by systematically comparing alternative algorithmic 
pathways and evaluating how pipeline bottlenecks change across embedded 
compute configurations, including GPU-based architectures.

Zhao et al.\ \cite{rs15225421} implement CUDA acceleration for a passive 
bistatic radar pipeline, reporting up to a 113.13$\times$ speedup over a CPU 
baseline across three algorithm stages. However, the study covers only clutter 
suppression, range--Doppler processing, and CA-CFAR detection, omitting angle 
estimation, coordinate transforms, and Kalman filtering, and does not discuss 
memory reallocation or thread synchronisation costs. This thesis addresses 
these gaps by benchmarking a more comprehensive algorithm selection and 
profiling host--device transfer and synchronisation overhead explicitly.

Zaknoun \cite{zaknoun2024_realtime_gpu_accelerated_radar_processing} provides 
a comprehensive treatment of GPU radar software architecture for real-time 
processing. However, this work is not situated in a UAV DAA context and does 
not evaluate performance under UAV SWaP constraints. This thesis adapts these 
architectural insights to the UAV DAA problem, evaluating how conclusions 
change under constrained power and memory budgets.

\section{Sensitivity and Detection in Low-SNR Regimes}

A key consequence of SWaP-constrained hardware is reduced aperture, which 
simultaneously lowers SNR and degrades angular resolution, increasing the 
likelihood that multiple targets occupy the same resolution cell.

An et al.\ 
\cite{an2024_time_varying_angle_estimation_unresolved_extended_targets_monopulse} 
propose an efficient method for resolving two unresolved targets within a 
single monopulse cell. However, evaluation is limited to simulated white-noise 
conditions, the method is not integrated into an end-to-end range--Doppler 
pipeline, and explicit failure modes exist for same-angle targets and 
cells containing three or more targets. This thesis addresses these gaps by 
testing the algorithm under non-white noise conditions and within a complete 
tracking pipeline, measuring the effect on track quality.

Aubry et al.\ 
\cite{aubry2020_single_pulse_simultaneous_detection_angle_estimation_multichannel} 
demonstrate that detection and angle estimation can be treated jointly in a 
multichannel array, increasing sensitivity to targets not visible in any single 
channel and avoiding the brittleness of early thresholding under low SNR. 
However, validation is limited to single simulated targets in Gaussian 
interference. This thesis addresses this gap by applying the algorithm to 
multiple targets under non-Gaussian noise regimes and measuring both 
sensitivity and track-quality impacts alongside compute cost.


\section{Summary and Research Gap}
Across the UAV DAA radar literature three gaps emerge. First, existing 
hardware demonstrations validate detection against large, high radar 
cross-section targets only; no work characterises sensitivity to small 
moving airborne targets under realistic encounter conditions. Second, 
processing feasibility on constrained embedded hardware has been demonstrated 
on FPGAs and ARM CPUs, but no work benchmarks a GPU-based pipeline in a UAV 
DAA context with comprehensive algorithm coverage and architectural profiling. 
Third, sensitivity algorithms for low-SNR monopulse radar exist but have only 
been validated under idealised white Gaussian noise with single targets, with 
no integration into complete pipelines or evaluation under realistic multi-target 
conditions.

This thesis addresses all three gaps by characterising detection and tracking 
sensitivity against small moving airborne targets, by benchmarking a 
comprehensive selection of radar processing and tracking algorithms on embedded 
GPU hardware with explicit profiling of host--device transfer and 
synchronisation overhead, and by evaluating monopulse sensitivity algorithms 
within a complete multi-target tracking pipeline under realistic noise conditions.