\section*{Statement of Contributions}

I, \textbf{Noah West}, declare that the intellectual content of this thesis is the product of my own work and that all assistance received in the preparation of this thesis and relevant sources have been appropriately acknowledged. The contributions I made to this research include:
\begin{itemize}
  \item Undertaking the background research and completing the literature review.
  \item Defining the research scope and developing the problem statement in consultation with my supervisor and the industry partner.
  \item Designing the methodology, experimental approach, and test plan with guidance from my supervisor.
  \item Designing and implementing, in collaboration with engineers from the industry partner \textit{Mission Systems}, the software pipeline described in this work.
  \item Profiling and evaluating the pipeline software to produce the reported results.
  \item Capturing radar data for use in testing and validation.
  \item Conducting the experiments, including configuration of the test setup and execution of data collection procedures.
  \item Performing analysis of results, including quantitative evaluation using appropriate metrics to validate conclusions.
  \item Interpreting findings, and writing the discussion and conclusions, incorporating feedback from my supervisor and relevant stakeholders.
  \item Writing the thesis and preparing figures, tables, and supporting material.
\end{itemize}

The above represents an accurate summary of my contribution.

\vspace{1.5em}

\noindent
\rule{0.45\textwidth}{0.4pt}\hfill
\rule{0.45\textwidth}{0.4pt}\\
\noindent
\textbf{Noah West}\hfill
\textbf{Dr.\ Donald Dansereau}\\
Honours Candidate\hfill
Senior Lecturer\\
School of Aerospace, Mechanical and\hfill
Australian Centre for Field Robotics,\\
Mechatronic Engineering,\hfill
The University of Sydney\\
The University of Sydney\hfill
\\
Date: \today \hfill
Date: \dotfill