\section{Case Studies}
\section{Case Studies: Learning Objectives Covered by Thesis}

For ESIPS substitution, this thesis is proposed to replace content from two elective units: \textbf{AMME5520 Advanced Control and Optimisation} and \textbf{ELEC3305 Digital Signal Processing}. The proposed thesis covers over 75\% of learning objectives from each unit outline through the necessary self-guided learning and engineering design required to meet the contributions.  

\subsection{Case Study 1: AMME5520 Advanced Control and Optimisation}

\subsubsection{LO1. \emph{Approach research papers in a professional and research-orientated manner, and conduct critical reviews of these papers}}
This learning objective is met through the thesis literature review and gap synthesis across UAV DAA radar pipelines, GPU radar processing, monopulse angle estimation under low SNR, and multi-target tracking. The thesis requires evaluating assumptions, identifying limitations, and justifying design choices based on evidence, aligning with Week 13 Lightning talks (LO1) and the unit’s self-directed critical engagement with research.

\subsubsection{LO2. \emph{Implement simple path generation algorithms, controllers and decision metrics for an autonomous system in order to meet specific mission objectives}}
This learning objective is met by implementing autonomy-relevant estimation and decision components in the detection-to-track chain: measurement formation, data association (e.g., NN/GNN/JPDA variants), tracking filters (EKF/UKF/IMM-style variants), and track lifetime management. Although the thesis project does not explicitly control the position of the targets that it is making estimations on, estimation is an essential component of any control system, and multi target tracking engages with the state based decision making that this learning objective is concerned with. The estimation theory in this project has heavy alignment with 
Weeks 07--08 in particular (Kalman filtering and extensions).

\subsubsection{LO3. \emph{Understand a number of different path generation and control algorithms implemented in autonomous systems and how they are linked to optimality criteria, platform stability and vehicle constraints.}}
Tracking aerial vehicles that can both fly in a straight line and conduct several manoeuvres motivates the use of multiple filters and tracks that model possible trajectories of the targets. Although targets are not being controlled, multi target tracking itself is an optimisation problem. Understanding stability is essential to minimise track id switching when multiple targets are within a few standard deviations of one another (in terms of state). \\

This learning objective is also met through the comparative evaluation of tracking algorithms, where we optimise for high track quality and low computational resource use. This aligns with Weeks 02--03 (optimality-driven algorithms), Weeks 07--09 (estimation, uncertainty, robustness).

\subsubsection{LO4. \emph{Understand how cost functions are used to define mission objectives in a mathematical form, so that autonomous systems can make decisions about their next action.}}
This learning objective is met by framing pipeline design as an objective-driven trade-off between sensitivity/track quality and computational cost, using ablations and parameter sweeps to identify design points. This aligns with Week 01 (optimal control framing), Weeks 10--11 (optimisation/MPC), and the unit’s focus on formal objective definition. Additionally, track association is an optimisation problem.  

\subsubsection{Coverage statement}
The thesis addresses LO1--LO4 through critical review, implementation of estimation/decision algorithms, comparative evaluation under constraints, and objective-driven trade-off analysis, demonstrating at least 75\% coverage.

\subsection{Case Study 2: ELEC3305 Digital Signal Processing}

\subsubsection{LO1. \emph{Describe signals using mathematical concepts such as convolutions, transforms, spectral analyses, linear difference equations, filters, correlation and covariance}}
This learning objective is addressed through frequency-domain radar processing. Convolutions will be used in the form of matched filters in the dechirping process. The Fourier transform will be applied with the FFT algorithm over both fast time and slow time to produce range and Doppler maps. Hann, Hamming, and other filters will be applied to minimise spectral leakage, and the spectral effect of our hardware configuration and geometry will be compensated for. Correlation, linear difference, and covariance will be essential concepts in the process of detection and tracking of targets. This aligns strongly with Week 03 (convolution and frequency response), Weeks 07--10 (DFT/FFT properties and spectral analysis), and the unit’s emphasis on transform-based signal description.

\subsubsection{LO2. \emph{Use software, such as MATLAB and Python, to develop code to analyse and process signals including filtering, inverse filtering, spectral analyses, resampling, time-frequency analyses}}
This learning objective is addressed through substantial software implementation and testing of DSP stages in an end-to-end pipeline, including benchmarking CPU vs GPU implementations and developing validation/profiling tools with parameter sweeps. This aligns with Weeks 02--12 practicals, which focus on implementing DSP in software. Python and C++ will be used to develop both the pipeline and the simulation application. 

\subsubsection{LO3. \emph{Identify linear signal models for time-invariant systems such as convolutional models, sinusoidal and harmonic models, echo and reverberation models, modulation models and time-frequency models.}}
This learning objective is addressed by using standard linear and time-frequency models for radar returns and mapping sampled signals into range--Doppler representations, then studying how model behaviour changes under low SNR and limited resolution. This aligns with Week 02 (signal models), Weeks 04--06 (DTFT/Z-transform/transfer functions), and Weeks 11--12 (sampling and ADC/DAC considerations).

\subsubsection{LO4. \emph{Design and evaluate signal processing systems.}}
This learning objective is addressed directly by designing and evaluating alternative pipeline configurations (windowing, FFT sizing/batching, CFAR variants, integration policies, and angle sensing), and quantifying effects on detection sensitivity, false alarms, and end-to-end latency/throughput. This aligns with Weeks 04--10 and the unit’s system design emphasis.

\subsubsection{Coverage statement}
The thesis covers LO1--LO4 through transform-based processing, software implementation, linear/time-frequency modelling, and end-to-end system design and evaluation, demonstrating at least 75\% coverage.
