\section{Performance Analysis}
\subsection{Throughput Analysis}
\todo{Measure in Bytes Per Second}
\subsection{Latency Analysis}
\todo{Use NSight}
\todo{Ablation Study}
\todo{Explore the effect of different hardware contexts on the performance. What contexts prevent us from implementing certain solutions and why}


\section{Performance Analysis}

\begin{itemize}
    \item This section evaluates the computational performance of the radar pipeline, focusing on throughput and latency.
    \item The aim is to determine whether the implemented algorithms are suitable for real-time UAV DAA applications.

    \item Throughput analysis measures how much data each implementation can process per unit time, reported in bytes per second.
    \item This shows whether the pipeline can sustain the required radar data rate.

    \item Latency analysis measures the time taken for data to pass through each stage of the pipeline and through the system as a whole.
    \item This is profiled using tools such as NVIDIA Nsight to identify bottlenecks, memory transfer costs, and kernel execution overheads.

    \item Variations of each operation are compared to understand the impact of different algorithmic choices and optimisations on performance. 
    \item An ablation study is used to evaluate the impact of individual optimisation choices by noting how the performance of the pipelines change when specific operations are removed from the process.
    \item This helps identify which design decisions provide meaningful performance gains, and where further optimisation efforts should be focused. A table will illustrate the latency and throughput contribution of each stage of the pipeline.  
    \item Performance is also compared across different hardware contexts to understand how architectural constraints affect implementation choices and runtime behaviour, e.g. physically unified memory vs managed memory.
    \item This informs which solutions are practical on embedded and GPU-based radar platforms.
\end{itemize}