\section{Tracking Application}
\label{sec:tracking_app}
\todo{Complete the following sections. How do the experiments resolve the gaps in the literature.}
% \subsection{Constant False Alarm Rate}
% \subsection{Monopulse Angle Sensing}
% \subsection{Embedding}
% \subsection{Polar Transform}
% \subsection{Data Ascociation}
% \subsection{Tracking Filters}
% \subsection{Initiating and Deleting}

\subsection{CFAR}
Constant False Alarm Rate (CFAR) detection is a key mechanism for resolving a map of noisy range data into discrete detections given a target false alarm rate. It does this by masking out any samples with magnitude below a threshold determined by the power of the samples around it. There are several variants of CFAR that each require consideration (see Figure \ref{fig:cfar}). Cell averaging (CA)-CFAR is the most appropriate for homogeneous sample data, greatest of (GO)-CFAR performs well with cluttered edges, smallest of (SO)-CFAR is suitable for multi target tracking, and ordered statistic (OS)-CFAR is appropriate for non-homogenous multi-target settings \cite{18645}. A sweep of window size and false alarm rate values will be conducted for each CFAR mode on real and simulated data and on the CPU and GPU. The performance (throughput, latency, memory, false alarm rate, sensitivity) will be compared across configurations in a cost benefit analysis. This addresses the literature gap in understanding how detection sensitivity and false alarm behaviour trade off against latency and throughput under SWaP constraints.

% \begin{figure}
%     \centering
%     \includesvg[width=0.7\linewidth]{Images/cfar_stacked_matched_colours}
%     \caption{Performance of four CFAR variants. Each algorithm registers a detection when its threshold is below the signal. The test signal has 5 peaks that are each surrounded by different noisy distributions. The bottom plot illustrates the detections made by each algorithm. OS-CFAR performs well in this example.}
%     \label{fig:cfar}
% \end{figure}

\subsection{Monopulse Angle Sensing}
Angle sensing converts multi-channel measurements into angle estimates that drive association and tracking. We will assess candidate angle discriminators by running controlled sweeps over SNR, channel imbalance, and multi-target proximity, and measuring angular bias, mean squared error, and confidence. The latency and throughput of CPU and GPU implementations will be measured. We will explicitly quantify the time and compute costs of stabilisation strategies such as sum-channel gating, regularised ratios, and calibration placement. The "Amplitude Angle Discriminator" and "Phase Angle Discriminator" methods will be compared for their computation requirements, angular bias and variance \cite{mitll_radar_lecture9_tracking_2008}. The algorithm will be validated on data obtained from flight tests. This addresses the gap in validating monopulse angle estimation methods beyond idealised simulations, which often assume Gaussian noise and clean single detections per target.  

\subsection{Polar Transform}
Because the radar have multiple receiver channels, each target detection will need to be rotated from the receiver's local polar coordinate from to the radar module's polar coordinate frame. We will also compare alternative polar-to-Cartesian transformation strategies in terms of numerical stability, computational cost, and their effect on downstream tracking accuracy. This addresses the gap in understanding how coordinate conversion choices influence both runtime performance and state estimation quality in real-time radar pipelines.

\subsection{Tracking Filter}
Filter choice determines how measurements are fused over time and how manoeuvres are handled. We will assess candidate filters by comparing extended Kalman filters (EKF) \cite{jazwinski1970stochastic}, unscented Kalman filters (UKF) \cite{julier1997newextension}, and interacting multiple models (IMM) \cite{blom1988imm} filters implemented on the CPU and GPU. Our evaluation metrics will include mean squared error (MSE), normalised estimation error squared (NEES), normalized innovation squared (NIS), latency, average time-to-confirm tracks, fragmentation \cite{hem2021maritime_mtt_metrics}, and ID-switch rate under clutter, missed detections, and unexpected manoeuvres. The evaluation will report how filter complexity translates into measurable improvements in track quality, and whether those gains justify the added costs.

\subsection{Data Association}
Data association assigns detections to existing tracks in multi-target scenarios. We will compare nearest neighbour (NN), global nearest neighbour (GNN) assignment, and joint probabilistic data association (JPDA) under sweeps of target density and clutter. Performance will be assessed using the "CLEAR MOT" metrics for multi-target tracking algorithms \cite{article} alongside computational metrics.

\subsection{Embedding}
The final radar pipeline must operate within the memory, power, and latency constraints of embedded hardware. We will evaluate how candidate pipeline designs transfer from desktop development platforms to embedded targets, measuring throughput, latency, memory use, and any loss in detection or tracking performance. This addresses the gap between algorithm validation in high-resource environments and practical deployment under SWaP-constrained UAV settings.

\subsection{Initiating and Deleting}
Track initiation and deletion logic strongly affects tracker stability, especially in cluttered scenes with missed detections and short-lived false alarms. We will compare alternative confirmation and deletion rules using metrics such as time-to-confirm, false track rate, fragmentation, and track persistence. This addresses the gap in understanding how track life-cycle design influences the balance between responsiveness and robustness in UAV radar tracking.