\section{Radar Processing}

\begin{itemize}
    \item Radar processing converts received echoes into target measurements such as range, velocity, and angle.
    \item Radar hardware performs transmission, reception, amplification, pulse-compression, downconversion, and analogue-to-digital conversion, while software extracts useful target information from sampled data.
    \item In software, a typical processing chain begins by organising the pulse-compressed samples across fast time, slow time, and antenna channels.
    \item By considering the samples the spectral domain (either with matched filtering or a fast time Fourier Transform), we can estimate the range of targets. 
    \item Optionally, a long time Fourier transform can be applied across slow time to estimate Doppler, which provides target radial velocity and helps separate moving targets from clutter. 
    \item Coherent integration across multiple pulses improves detectability of weak targets. This involves summing the complex samples across pulses.
    \item After integration detection algorithms such as Constant False Alarm Rate (CFAR) can identify candidate target returns, which are then passed to angle estimation and tracking stages. 
    \item The bearing and elevation of targets can be estimated using monopulse processing, which compares the received signal across multiple antenna channels to infer angle with high accuracy.
    \item The resulting range, Doppler, and angle measurements form the basis for later tracking and classification stages in a DAA system.
\end{itemize}